---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
library(voteviewr)
options(width = 90)
```

# voteviewr

<!-- badges: start -->
[![Travis build status](https://travis-ci.org/r-congress/voteviewr.svg?branch=master)](https://travis-ci.org/r-congress/voteviewr)
[![AppVeyor build status](https://ci.appveyor.com/api/projects/status/github/r-congress/voteviewr?branch=master&svg=true)](https://ci.appveyor.com/project/r-congress/voteviewr)
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)
[![CRAN status](https://www.r-pkg.org/badges/version/voteviewr)](https://CRAN.R-project.org/package=voteviewr)
<!-- badges: end -->

Get data from [Voteview.com](https://voteview.com/data)

## Installation

You can install the released version of voteviewr from [CRAN](https://CRAN.R-project.org) with:

``` r
install.packages("voteviewr")
```


You can install the dev version of voteviewr from [Github](https://github.com) with:

``` r
if (!requireNamespace("remotes")) {
  install.packages("remotes")
}
remotes::install_packages("r-congress/voteviewr")
```

## Import

Import Voteview data from the House and Senate for the 116th U.S. Congress

```{r}
## read using defaults (both chambers of current congress)
cng116 <- read_voteview()
```

or get data from the House and Senate separately for the 115th U.S. Congress

``` r
## house 115th data
h115 <- read_voteview("house", 115)

## senate 115th data
s115 <- read_voteview("senate", "115th")
```

or specify a session of Congress

``` r
## both chambers of 99th Congress
cng99 <- read_voteview(99)

##
cng99 <- read_voteview(99, "senate")
```

or specify a year

``` r
## get data on the 99th Congress
cng1961 <- read_voteview(1961)
```


## Data

A tibble is returned

```{r}
## preview tibble
cng116
```

More info on all returned variables

```{r}
## view object structure
str(cng116)
```
